mlr_assg4

### 2022-09-20 hw4-1/abhinav/mlr.Rmd
MLR code update

### Corealtion
cormat <- round(cor(crime_data),2)
cormat[upper.tri(cormat)] <- NA
melted_cormat <- melt(cormat)
# plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2,
                                   fill=value)) +
geom_tile() +
geom_text(aes(Var1, Var2, label = value),
          color = "white", size = 3)
```
## Observations: 
Wealth and Income Inequality are 2 highly correlated variables (-ve correlation) ,  hence we'll pick only 1 out of 2 
Po1 and Po2 are 2 correlated variables , hence we'll pick only 1 out of 2 
Same goes for U1 and U2, , hence we'll pick only 1 out of 2

@@

```{r}
crime_data$So<-as.factor(crime_data$So)
# Linear Regression model with all features
lmodel_1<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data)
summary(lmodel_1)

# Linear Regression Model with Limited features (removing highly correlated features)
lmodel_2<-lm(Crime~M+So+Ed+Po1+LF+M.F+Pop+NW+U1+Ineq+Prob+Time,data=crime_data)
summary(lmodel_2)

```{r}
par(mfrow = c(2, 2))
plot(lmodel_2)
```

>>>>

### Corealtion
cormat <- round(cor(crime_data),2)
cormat[upper.tri(cormat)] <- NA
melted_cormat <- melt(cormat)
# plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2,
                                   fill=value)) +
geom_tile() +
geom_text(aes(Var1, Var2, label = value),
          color = "white", size = 3)
```
## Observations: 
Wealth and Income Inequality are 2 highly correlated variables (-ve correlation) ,hence we can 1 variable out of both
Po1 and Po2 are 2 correlated variables , hence we can pick only 1 out of 2 
Same goes for U1 and U2, , hence we can pick only 1 out of 2

@@

```{r}
options(scipen=999)
crime_data$So<-as.factor(crime_data$So)
# Linear Regression model with all features
lmodel_1<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data)
summary(lmodel_1)
# plotting the residuals to check for assumptions in the plain vanilla model with all features
par(mfrow = c(2, 2))
plot(lmodel_1)
```

```{r}
# removing all the potential outliers/influential points
crime_data_wo<-crime_data[-c(11,46,29),]
dim(crime_data_wo)
# Linear Regression model with all features on the reduced dataset
lmodel_1<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_1)
```

```{r}
# Linear Regression Model with Limited features (removing highly correlated features)
lmodel_2<-lm(Crime~M+So+Ed+Po1+LF+M.F+Pop+NW+U1+Ineq+Prob+Time,data=crime_data)
summary(lmodel_2)

par(mfrow = c(2, 2))
plot(lmodel_2)
```
